Uncovering underlying high-level musical content in the time domain \\ \small Leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn deep audio embeddings with applications to boundary detection tasks

### 2023-06-29 results/subsections/tables.tex
Updates from Overleaf

\begin{table}
  \centering
  \begin{adjustbox}{width=\textwidth}
  \begin{threeparttable}
    \begin{tabular}{c|l|c|c|c} 
\toprule
     \multicolumn{2}{c|}{\textbf{Training dataset} and \textbf{Feature}}  & \multicolumn{1}{c}{\textbf{SF}} & \multicolumn{1}{c}{\textbf{Foote}} & \multicolumn{1}{c}{\textbf{CNMF}} 
     \\ \midrule 
    \multirow{5}{*}{}&   
         \multirow{1}{*}{MFCC } & \usebox{\mfccSF} & \usebox{\mfccFoote} & \usebox{\mfccCNMF} \\\cline{2-5}
        & \multirow{1}{*}{PCP} & \usebox{\pcpSF} & \usebox{\pcpFoote} & \usebox{\pcpCNMF} \\\cline{2-5}
        & \multirow{1}{*}{Tonnetz} & \usebox{\tonnetzSF} & \usebox{\tonnetzFoote} & \usebox{\tonnetzCNMF} \\\cline{2-5} 
        & \multirow{1}{*}{CQT} & \usebox{\cqtSF} & \usebox{\cqtFoote} & \usebox{\cqtCNMF} \\\cline{1-5} 
    \multirow{1}{*}{GTZAN}& 
        \multirow{1}{*}{Embeddiogram} & \usebox{\embeddioaSF} & \usebox{\embeddioaFoote} & \usebox{\embeddioaCNMF} \\\cline{1-5} 
    \multirow{1}{*}{MSD}& 
        \multirow{1}{*}{Embeddiogram} & \usebox{\embeddiobSF} & \usebox{\embeddiobFoote} & \usebox{\embeddiobCNMF} \\\bottomrule
    \end{tabular}
    \caption[Metric comparison for different audio features]{Comparison of precision, recall, and f-measure for different features obtained using the SF, Foote, and CNMF algorithms \cite{sf} \cite{foote} \cite{cnmf} on the SALAMI dataset. Sliding windowed segments across the audio signal input signal is 4 seconds}\label{ta:results}
  \end{threeparttable}
  \end{adjustbox}
\end{table}

>>>>

\begin{table}
  \centering
  \begin{adjustbox}{width=\textwidth}
  \begin{threeparttable}
    \begin{tabular}{c|l|c|c|c} 
\toprule
     \multicolumn{2}{c|}{\textbf{Training dataset} and \textbf{Feature}}  & \multicolumn{1}{c}{\textbf{SF}} & \multicolumn{1}{c}{\textbf{Foote}} & \multicolumn{1}{c}{\textbf{CNMF}} 
     \\ \midrule 
    \multirow{5}{*}{}&   
         \multirow{1}{*}{MFCC } & \usebox{\mfccSF} & \usebox{\mfccFoote} & \usebox{\mfccCNMF} \\\cline{2-5}
        & \multirow{1}{*}{PCP} & \usebox{\pcpSF} & \usebox{\pcpFoote} & \usebox{\pcpCNMF} \\\cline{2-5}
        & \multirow{1}{*}{Tonnetz} & \usebox{\tonnetzSF} & \usebox{\tonnetzFoote} & \usebox{\tonnetzCNMF} \\\cline{2-5} 
        & \multirow{1}{*}{CQT} & \usebox{\cqtSF} & \usebox{\cqtFoote} & \usebox{\cqtCNMF} \\\cline{1-5} 
    \multirow{1}{*}{GTZAN}& 
        \multirow{1}{*}{Embeddiogram} & \usebox{\embeddioaSF} & \usebox{\embeddioaFoote} & \usebox{\embeddioaCNMF} \\\cline{1-5} 
    \multirow{1}{*}{MSD}& 
        \multirow{1}{*}{Embeddiogram} & \usebox{\embeddiobSF} & \usebox{\embeddiobFoote} & \usebox{\embeddiobCNMF} \\\bottomrule
    \end{tabular}
    \caption[Metric comparison for different audio features and different segmentation algorithms]{Comparison of precision, recall, and f-measure for different features obtained using the SF\cite{sf}, Foote \cite{Foote2000AutomaticNovelty}, and CNMF \cite{NietoCONVEXIDENTIFICATION} algorithms on the SALAMI dataset. Sliding windowed segments across the audio signal input signal is 4 seconds}\label{ta:results}
  \end{threeparttable}
  \end{adjustbox}
\end{table}
